DATA 605 Week 13

### 2019-04-23 DATA605/MSilva_Assign13.Rmd
Completed Question 3

@@

**Find the total area of the red rectangles in the figure below, where the equation of the line is f(x) = 2x-9.**

>>>>

$$\int{-\frac{3150}{t^4}-220 dt}\rightarrow-220t-3150\frac{1}{-3t^3}\rightarrow-220t+\frac{1050}{t^3} + C$$

To solve for the constant we solve for $C$ given that $N(t) = 6530$

$$6530 = -220(1)+\frac{1050}{(1)^3} + C \rightarrow 6530 = -220 + 1050 + C \rightarrow 6530 = 830 + C \rightarrow 5700 = C$$

The function is $N(t)=\frac{1050}{t^3}-220t+5700$

@@

**Find the total area of the red rectangles in the figure below, where the equation of the line is $f(x) = 2x-9$.**

![](MSilva_Assign13_Q3.png)

The area under the line is a triangle from 4.5 to 8.5.  The height is found by pluging 8.5 into the function.

$$f(8.5)=2(8.5)-9=17-9=8$$

The area of the triangle is 1/2 base x height so

$$\frac{1}{2}(8.5 - 4.5) \times 8 = \frac{1}{2}(4) \times 8 = 2 \times 8 = 16$$

So the area is 16.  Verifying with R

```{r, comment=NA}
fx <- function(x){
  2*x-9
}
integrate(fx, 4.5, 8.5)
```
